---
title: 'Simulation: Dominant Hand'
author: "Audrey Le Meur"
date: "10/6/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In these notes, we will be learning different ways to simulate by using the example of dominant hand. At first, we will be assuming that people can be either right-handed or left-handed, and later we will consider ambidexterity.

## Simulation of a binomial

Let's simulate the number of left handed people in 1000 simulations.

```{r binom}
nsims = 1000
nobs = rep(NA, nsims)
nobs = rbinom(nsims, 14, 0.10)

hist(nobs)
```

## Simulation of a class-sized sample

First, we're going to run our simulation with 14 people (sample size), about the size of our class.

```{r class}
nsample = 14
nobs = rbinom(nsims, nsample, 0.10)
hist(nobs)
```

## Simulation of a large-size sample

Next, let's try a much larger sample size.

```{r}
nsample = 331037
nobs = rbinom(nsims, nsample, 0.10)
hist(nobs)
```

## Comparing sample sizes

The class-sized sample and the large-size sample differ in shape. The large-size sample will also be shifted away from zero. Notice how the large-size sample is also more similar to a normal distribution.

## Simulation of a medium-size sample

Now let's look at a simulation with sample size in-between our first two examples. Notice how this one also looks like a normal distribution centered at about 10.
```{r}
nsample = 100
nobs = rbinom(nsims, nsample, 0.10)
hist(nobs)
```

## Accounting for Ambidexterity