---
title: 'Regression and Other Stories: Fake midterm and final exam'
author: "Andrew Gelman, Jennifer Hill, Aki Vehtari"
date: "`r format(Sys.Date())`"
output: pdf_document
---
Fake dataset of 1000 students' scores on a midterm and final
exam. See Chapter 6 in Regression and Other Stories.

-------------


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, error=FALSE, warning=FALSE, comment=NA)
# switch this to TRUE to save figures in separate files
savefigs <- FALSE
```

**Load packages**

```{r }
library("rstanarm")
```

## Simulate fake data

We want to create a fake data simulation to demonstrate regression towards the mean. First, we will simulate the true ability of 1000 students and then simulate the noise for each exam. Lastly, we will combine the simulations of each exam into one data frame.

```{r }
n <- 1000
# set the random seed to get reproducible results
# change the seed to experiment with variation due to random noise
set.seed(2243)
true_ability <- rnorm(n, 50, 10)
noise_1 <- rnorm(n, 0, 10)
noise_2 <- rnorm(n, 0, 10)
midterm <- true_ability + noise_1
final <- true_ability + noise_2
exams <- data.frame(midterm, final)
```

## Linear regression

Now, let's find the linear regression when we compare the midterm to the final exam scores.

*Note:* The option `refresh = 0` supresses the default Stan sampling progress output. This is useful for small data with fast computation. For more complex models and bigger data, it can be useful to see the progress.

```{r }
fit_1 <- stan_glm(final ~ midterm, data=exams, refresh = 0)
print(fit_1, digits=2)
```

The slope is not equal to 1 because of regression to the mean. If you had an extreme value on the midterm, you are more likely to draw a score closer to the mean on the next observation.

## Transforming the linear regression

We can give the intercept a more useful interpretation by transforming the linear regression. In this case, we want to subtact the mean of the midterm exams from each midterm exam score.

```{r }
fit_2 <- stan_glm(final ~ I(midterm-50), data=exams, refresh = 0)
print(fit_2, digits=2)
```

We can interpret this to mean that when a midterm exam score is equal to the midterm mean, then the same person's final exam score would be 50.1. 

Now, let's look at the confidence interval for this linear regression:

```{r}
summary(fit_2)
```

While this doesn't align with the frequentist approach in our textbook, we can use the confidence interval to estimate a reasonable range of values of the slope and the intercept. So the reasonable values for intercept are (49.8, 50.7) and a reasonable value for the slope is 0.5.

## Plot midterm and final exam scores

```{r eval=FALSE, include=FALSE}
if (savefigs) pdf(here("FakeMidtermFinal/figs","FakeMidtermFinal1.pdf"), height=4, width=4)
```
```{r }
par(mar=c(3, 3, 2, 1), mgp=c(1.7, .5, 0), tck=-.01)
par(pty="s")
plot(midterm, final, xlab="Midterm exam score", ylab="Final exam score", xlim=c(0,100), ylim=c(0,100), xaxs="i", yaxs="i", xaxt="n", yaxt="n", pch=20, cex=.5)
x <- seq(0,100,20)
axis(1, x)
axis(2, x)
for (i in x){
  abline(h=i, col="gray70", lty=2)
  abline(v=i, col="gray70", lty=2)
}
abline(coef(fit_1))
```
```{r eval=FALSE, include=FALSE}
if (savefigs) dev.off()
```

