---
title: 'Fit a Model: Health Expenditure'
author: "Audrey Le Meur"
date: "9/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading a Table

First, we want to read the data from the file. To do that, we will use the R method read.table.

```{r read}
healthdata <- read.table(file = "data/healthdata.txt", header = TRUE)
head(healthdata)
```

* if you're curious on how to take in text, look at the very first ROAS example for scatterplots.

## Plot the Data

Next, we will the plot the data that we read from the table.

```{r plot}
plot(lifespan~spending, data=healthdata)
```

## Fit the Model

Last, we will fit the data to a linear model. To do this, we will use the R method lm.

```{r fit}
m1 <- lm(lifespan~spending, data=healthdata)
m1
```

Now that we have created our model, let's plot it on the same plot as the data. We'll use the R methods coef and abline as well as the previously mentioned plot.

```{r modelanddata}
ab <- coef(m1)
plot(lifespan~spending, data=healthdata)
abline(ab)
```

## Eliminate an Outlier

There's one more thing we can do to improve our model: eliminate an outlier. We can do this manually using the R subset method since we can see that USA is the outlier point. Then, we will plot the new model on the data.

```{r outlier}
m2 <- lm(lifespan~spending, data=subset(healthdata, country != "USA"))
ab <- coef(m2)
plot(lifespan~spending, data=healthdata)
abline(ab)
```

While this is still interesting to look at, it would be even more useful to plot both models on the same plot. Each model's line should have a different color so we can distinguish them on the plot.

```{r twomodels}
ab1 <- coef(m1)
ab2 <- coef(m2)
plot(lifespan~spending, data=healthdata)
abline(ab1, col="blue")
abline(ab2, col="red")
```

