---
title: "Basic Methods"
author: "Audrey Le Meur"
date: "9/29/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Weighed Averages

First, read the data from the table and summarize the data frame.

```{r read}
d <- read.table("weighted.txt", header=TRUE)
str(d)
```

Next, let's look at a specific vector using $. We can also manipulate that vector just like real numbers.

```{r vector}
d <- read.table("weighted.txt", header=TRUE)
d$n_trial
d$n_trial/90
```

Now, we can assign a new column to our original data frame using that vector manipulation. Then, use those weights to calculate the weighted average.

```{r new}
d <- read.table("weighted.txt", header=TRUE)
d$w <- d$n_trial/90
d
mean(d$w*d$mn_rt)
```

## Plotting averages

Now, we will reference a sleep study from the library lattice.

```{r}
library(lme4)
str(sleepstudy)
```

Now let's plot the average reaction of each participant over time. We can also add a linear regression line.

```{r}
library(lme4)
d <- sleepstudy
plot(Reaction~Days, data=d)
m1 <- lm(Reaction~Days, data=d)
abline(coef(m1))
```

Another way we can look at the data is to plot each participant individually.

```{r}
library(lattice)
library(lme4)
d <- sleepstudy
xyplot(Reaction~Days|Subject, data=d)
```

