---
title: "Chapter 9 Example"
author: "Audrey Le Meur"
date: "10/20/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating a table of means and standard deviation

First, we want to create two tables: one with the means and one with the standard deviations. We'll use the R method tapply. tapply takes three parameters:x, the index, and the function. X is the data points that we want to summarize. The index is a list of the independent variables. The function is the summary statistic we want to apply (mean or standard deviation).

```{r}
d = read.table("ch-9-example.txt", header=TRUE)
tapply(d$prop_cor, 
       INDEX=list(d$study,d$test), 
       FUN=mean)
tapply(d$prop_cor, 
       INDEX=list(d$study,d$test), 
       FUN=sd)

```

These two lines give us a summary of the distributions of each of the four conditions.

## Main effect of study

We could also look at the effect of the different test/study types.

```{r}
d = read.table("ch-9-example.txt", header=TRUE)
tapply(d$prop_cor, 
       INDEX=list(d$study), 
       FUN=mean)
```

This is not really useful in this case because there is an interaction between study and test. Therefore, we should analyze every combination of test and study.

## Analysis of Variance

To run an analysis of variance, we use the R method aov.

```{r}
d = read.table("ch-9-example.txt", header=TRUE)
m1 = aov(prop_cor~study*test, data=d)
summary(m1)
```

Notice how small the p-value is. The p-value here means that the effect of study format depends on the level of test format.

## Linear model

To make a linear model, lm has to transform our nominal categories into 0 and 1 coefficients before 

```{r}
d = read.table("ch-9-example.txt", header=TRUE)
m2 = lm(prop_cor~study*test,data=d)
m2
```

The intercept represents the mean when both the test type and the study type are pictures. "studywrd" and "testwrd" represent the difference from the intercept when the study type is changed to words and the test type is changed to words respectively. Lastly, "studywrd:testwrd" is added to the three previous values to represent the mean when both the test and study type are words.

## STAN model

```{r}
library(rstanarm)
m3 = stan_glm(prop_cor~study*test, data=d, refresh=0)
m3
```

## STAN logistic model

We want to use a logistic model because all three other models analyzes binomial data using Gaussian models. The logistic transformation allows linear methods to be applied to proportion data (which is bounded by 0 and 1).

```{r}
m4 = stan_glm( cbind(prop_cor, 100-prop_cor)~study*test,
               data=d,
               family=binomial("logit"),
               refresh=0)
m4
```

We need to use inverse logistic to turn our results back into a proportion. *(need to go back to the recording and figure out what's going on here)*

```{r}
coef(m4)
invlogit(1.9173394)
invlogit(1.9173394-1.4587607)
invlogit(1.9173394-0.8815533)
invlogit(1.9173394-1.4587607-0.8815533+1.9172186)
```

